Let's talk about Thurstone \& Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2024-11-22 _tex/index.tex
Built site for gh-pages

In contrast, the assumption of \emph{equal dispersion between stimuli}
suggests that the variability in the perceived trait level of the
stimuli is the same across stimuli. While Thurstone acknowledged that
this assumption may be violated when ``dealing with less conspicuous
attributes or with less homogeneous stimuli''
\citep[pp.~374]{Thurstone_1927a}, no study explicitly proposes that this
assumption could also be violated due to the presence of an additional
hierarchical (grouping) structure relevant to the texts. One such
scenario might arise, for example, when comparing texts produced by
university and secondary school students. In this case, university
students may consistently (or more precisely) produce higher-quality
texts, while secondary school students, who exhibit a broader range of
writing abilities, would show greater variability in the quality of
their texts. Although this example is somewhat contrived, it effectively
illustrates how assuming equal dispersions across texts can overlook
meaningful differences in the reliability of text quality across groups
or individuals.

>>>>

In contrast, the assumption of \emph{equal dispersion between stimuli}
suggests that the variability in the perceived trait level of the
stimulus is the same across stimuli. While Thurstone acknowledged that
this assumption may be violated when ``dealing with less conspicuous
attributes or with less homogeneous stimuli''
\citep[pp.~374]{Thurstone_1927a}, no study explicitly proposes that this
assumption could also be violated due to the presence of an additional
hierarchical (grouping) structure relevant to the texts. One such
scenario might arise, for example, when comparing texts produced by
university and secondary school students. In this case, university
students may consistently (or more precisely) produce higher-quality
texts, while secondary school students, who exhibit a broader range of
writing abilities, would show greater variability in the quality of
their texts. Although this example is somewhat contrived, it effectively
illustrates how assuming equal dispersions across texts can overlook
meaningful differences in the reliability of text quality across groups
or individuals.
